\textbf{\sc Deliberative Autonomy for Marine Robotics}

### 2012-02-02 trunk/europa.tex
checkpoint. more europa content.

EUROPA is a general purpose AI planning toolkit developed at NASA Ames.  Automated Planning can be reformulated as a constraint satisfaction problem (TODO: ref). EUROPA is an extension of that idea, however, unlike other approaches where the entire planning problem is translated into a CSP and then solved using traditional CSP methods, EUROPA uses a constraint reasoning engine as a fundamental building block, and enriches it with other architectural components that allow a more direct mapping for scheduling and planning problems, which in turn allows easier development of efficient solving methods.

@@

Planning:
In the Shopping Agent Problem (TODO: ref to Norvig) an agent needs to purchase a set of products that are available at specific locations (supermarket, hardware store, etc), the agent  is subject to temporal (must complete tasks by specific deadlines) and resource (fuel, carrying capacity, etc) constraints. The agent must figure out what actions need to be performed to find and acquire the required items, as well as when to perform each of those actions.

@@

These relationships between Planning, Scheduling and Constraint Satisfaction have been examined in detail in the literature (TODOL ref Frank et al on Planning vs. Scheduling), and they lead to EUROPA's use of constraint reasoning as its innermost building block. Next we will examine the main ideas from Constraint Satisfaction Programming, and from Constraint Based Planning and Scheduling that constitute EUROPA's theoretical underpinnings, then we dive into how EUROPA implements those ideas.

@@

There has been 
State Variable representation

CSP encodings

Constraint Based and interval planning.

@@

@@

Dynamic Objects

TODO (there was a stub in the old doxygen docs for this)
Timelines

@@

TODO: explain variable, object, predicate and action types, including constraints that can be part of them

@@

\begin{enumerate}
	\item Variable Types: This model uses integer (activity duration, start and end times, etc) and string (Location and Product names, etc)
	\item Object Types:
	\item Predicate Types:
	\item Action Types:
\end{enumerate}

>>>>

Planning, for our purposes, can be thought of as determining all the small tasks that must be carried out in order to accomplish a goal. Let's say your goal is to buy a gallon of milk. It may sound like a simple task, but if you break it down, there are many small tasks involved: obtain keys, obtain wallet, start car, drive to store, find and obtain milk, purchase milk, etc. Planning also takes into account rules, called constraints, which control when certain tasks can or cannot happen. Two (of many) constraints in this example are that you must obtain your keys and wallet before driving to the store and you must obtain the milk before purchasing it.

Here is what a simple plan for buying milk at the store might look like:

EUROPA is a general purpose AI planning toolkit developed at NASA Ames.  
TODO: Talk about NASA missions where EUROPA has been used.

@@

Planning:
In the Shopping Agent Problem (TODO: ref to Norvig) an agent needs to purchase a set of products (milk, drill, etc) that are available at specific locations (supermarket, hardware store, etc), the agent  is subject to temporal (must complete tasks by specific deadlines) and resource (fuel, carrying capacity, etc) constraints. The agent must figure out what actions need to be performed to find and acquire the required items, as well as when to perform each of those actions.

@@

These relationships between Planning, Scheduling and Constraint Satisfaction have been examined in detail in the literature (TODOL ref Frank et al on Planning vs. Scheduling), and they lead to EUROPA's use of constraint reasoning as its innermost building block. Below we examine the main ideas from Constraint Satisfaction Programming, and from Constraint Based Planning and Scheduling that constitute EUROPA's theoretical underpinnings, then we dive into how EUROPA implements those ideas.

@@

The most common planning formulations use a propositional representation, where the state of the world is represented by a set of propositions (statements that can be true or false), and operators change the truth values of these propositions (TODO ref?). Although these formulations are powerful and have allowed researchers to develop numerous contributions in automated planning, there are many classes of problem domains that are difficult it is difficult to represent using them.

In particular, it is hard to represent time, resources, mutual exclusion and concurrency using propositions (TODO: ref?).  It is straightforward to represent and reason about all of those elements using a CSP representation, as a result there has been some work on doing automated planning while taking advantage of CSP  (TODO: ref).  Traditionally, the entire planning problem is translated into a CSP and then solved using traditional CSP methods, this leads to a formulation where action choices and relationships are represented as variables and/or constraints. However, this has at least two major drawbacks:
\begin{enumerate}
	\item Given that action choices and relationships (rules) are expresed through variables, the domain descriptions that result from this approach are not intuitive and therefore difficult to understand and debug
	\item If the structure of a planning model (actions, conditions, effects, dependencies at the action level, etc) is not explicitly maintained by the CSP planner, the search algorithms are deprived of critical information to make better decisions. If that structure is maintained somehow (for instance, by internally marking variables that represent action choice and relationships between actions), it is still hard to write search algorithms as any planning-specific insight has to be translated into the CSP representation of variables and constraints  (TODO: example?)
\end{enumerate}

Constraint-Based Attribute and Interval planning (CAIP) (TODO:ref) is intended to close that gap: on the one hand, it takes advantage of a CSP representation, but it also uses attributes and intervals to maintain an explicit representation of the elements relevant to planning, so that it is easier to write algorithms that search for an reason abut plans. The main elements of CAIP are:

\begin{enumerate}
	\item Intervals:
	\item Attributes:
	\item Domain Constraints an Configuration rules:
\end{enumerate}

TODO: Explain how planning problem instances and their solutions are represented.

@@

EUROPA is an implementation of the CAIP framework explained in the previous section

@@

Timelines

@@

@@

TODO: explain variable, object, predicate and action types, including constraints that can be part of them
\begin{enumerate}
	\item Variable Types: This model uses integer (activity duration, start and end times, etc) and string (Location and Product names, etc)
	\item Object Types:
	\item Predicate Types:
	\item Action Types:
\end{enumerate}
